|

### 2022-01-26 replication_paper/IntroducingICBe_DouglassEtAl_2021_BetaDraft_bookdown.Rmd
paper rmds
pruned

TLS = FALSE
```

@@

  parsed %>% saveRDS(paste0(here::here(), "/replication_data/temp/parsed.Rds"))

  entities <- entity_extract(parsed, type = "all")
  entities %>% saveRDS(paste0(here::here(), "/replication_data/temp/entities.Rds"))

} else {
  parsed <- readRDS(paste0(here::here(), "/replication_data/temp/parsed.Rds"))
  entities <- readRDS(paste0(here::here(), "/replication_data/temp/entities.Rds"))

@@

if(!TLS){
downloaded_file <- googledrive::drive_download(file="https://docs.google.com/spreadsheets/d/1a7Id0Zg41PTKEv74H_KjiJzhMak2jGh0leT7B8oVWdI/edit#gid=0", path=target_file, type = "xlsx", overwrite=T)
}
dictionary_actors    <- readxl::read_excel(target_file, sheet="actors")
actor_translator    <- readxl::read_excel(target_file, sheet="actor_translator")

@@

ym   4
wordnet_rdf <- readRDS(paste0(here::here(), "/replication_data/in/wordnet_rdf.Rds") )

@@

  verbs_sentence_wordnet <- readRDS(paste0(here::here(),"/data_replication/temp/verbs_sentence_wordnet.Rds"))

>>>>

TLS = TRUE
```

@@

  parsed %>% saveRDS(paste0(here::here(), "/replication_paper/data/temp/parsed.Rds"))

  entities <- entity_extract(parsed, type = "all")
  entities %>% saveRDS(paste0(here::here(), "/replication_paper/data/temp/entities.Rds"))

} else {
  parsed <- readRDS(paste0(here::here(), "/replication_paper/data/temp/parsed.Rds"))
  entities <- readRDS(paste0(here::here(), "/replication_paper/data/temp/entities.Rds"))

@@

dictionary_actors    <- readxl::read_excel(target_file, sheet="actors")
actor_translator    <- readxl::read_excel(target_file, sheet="actor_translator")

@@

wordnet_rdf <- readRDS(paste0(here::here(), "/replication_paper/data/in/wordnet_rdf.Rds") )

@@

  verbs_sentence_wordnet <- readRDS(paste0(here::here(),"/replication_paper/data/temp/verbs_sentence_wordnet.Rds"))
